PyPy's Approach to Virtual Machine Construction

### 2006-05-31 talk/dls2006/paper.tex
cpython 2.4.3 ref
no ref for Richards at the moment

The tool-chain has been tested with and can sucessfully apply
transformations enabling various combinations of features. The
translated interpreters are benchmarked using pystone (a Dhrystone 2.0
\cite{dhry20} derivative traditionally used by the Python community, although it is
a rather poor benchmark) and the classical [Richards] benchmark and
compared against [CPython] 2.4.3 results and are summarized in table
\ref{perfsumm}.

>>>>

The tool-chain has been tested with and can sucessfully apply
transformations enabling various combinations of features. The
translated interpreters are benchmarked using pystone (a Dhrystone 2.0
\cite{dhry20} derivative traditionally used by the Python community,
although it is a rather poor benchmark) and the classical Richards
benchmark (ported to Python) and compared against CPython 2.4.3 \cite{cpy243}
results and are summarized in table \ref{perfsumm}.
